US Korea Exchange Rates \\ STA206 Final Project

### 2014-12-11 paper.tex
reproducibility section

In today's highly connected global society people and money move between
countries. The exchange rates between countries determine the value of
that currency.

@@

If one plans to go on vacation in a foreign country then it makes sense to
visit a country where the exchange rate is favorable.

\subsection{Data}
We use data from Quandl.com, a service that provides clean, documented
data from a wide variety of sources including the US Federal Reserve,
World Bank, and the National Bank of Korea. 
{\tt Exchange rate} between Korean Won and US dollar is the primary $Y$
variable.

@@

\subsection{Data Collection}
The data is loaded directly using a
web API (Application programming interface).
Using this service will make it easier to repeat the analysis in the future, or conduct similar analyses between
different countries.

>>>>

In today's highly connected global society people and money move between
countries. The exchange rates between countries determine the relative
value of that money.

@@

\subsection{Data}

We use data from Quandl.com, a service that provides clean, documented
data from a wide variety of sources including the US Federal Reserve,
World Bank, and the National Bank of Korea. 
{\tt Exchange rate} between Korean Won and US dollar is the primary $Y$
variable.

@@

\subsection{Dynamic Data}

The data used in this analysis is unusual- it's generated dynamically from
live, high quality sources, and is self updating. The data is loaded directly from Quandl using a REST (Representational 
State Transfer) web API (Application programming interface), and then
cached locally, limiting network dependence.
Using this service makes it easy to repeat the analysis in the future, or conduct similar analyses between
different countries.

\subsection{Reproducibility}

Above we mentioned that the data and all analysis in the report is self 
updating. This is accomplished through the use of GNU \texttt{make}, which
describes a DAG (Directed Acyclic Graph) of dependencies for the final
report. \texttt{make} detects file modifications and will lazily run all
commands and scripts required for the final output.

What does this mean? Suppose that we need more variables to do the
regression. Thanks to the use
of industry standard ISO codes for the countries and proper parameters in
our code base this becomes a simple task.
We've stored string templates for the country level 
variables in a file
called \texttt{template.txt}. The data collection and preprocessing steps
are automated, so we can add more variables simply by adding a row to
\texttt{template.txt} and entering the command \texttt{make} from the shell
prompt, which causes the following sequence of events:

\begin{enumerate}
    \item \texttt{make} detects the changed template file
    \item The script \texttt{download.R} runs, updating the cache
    \item The script \texttt{preprocess.R} runs, applying the appropriate
        transformations and joining the tables to a form suitable for
        analysis
    \item All other scripts which depend on the preprocessed data run
    \item The report output is produced
\end{enumerate}

In this case the output is a PDF, but it could just as easily be a web page
on the department server, or an upload into another REST API.

If we were doing this analysis for a client and need to run it again a year
later with a new year of data 
then all we have to do is type \texttt{make}. We'll still need to interpret
plots and models, but the most time consuming work is done.

One other aspect of reproducibility is version control. In this
project we've used \texttt{Git} to collect snapshots of the project at
every stage. The project is hosted publicly on
Github\footnote{\url{https://github.com/clarkfitzg/stats206\_project}}.
A look at the log file shows what work happened when and why,
which is important for establishing provenance. In particular it shows 
that we've been active on this project every day since
December 1st. Here's an example of a log entry:

\begin{verbatim}
commit e2beaf01b0a1457e7167989c1fae575c2a676f19
Author: Clark Fitzgerald <clarkfitzg@gmail.com>
Date:   Mon Dec 8 20:51:04 2014 -0800

    implemented local caching, decoupled download step
\end{verbatim}
The point is that through a little engineering the data analysis process
can be made transparent, automated, extensible, and fully reproducible.
